### 2022-01-26 input/abstract.tex
mostly about abstract intro

\begin{abstract}
  %% Context and problem
  Although the holy grail to store and manipulate data in Edge
  infrastructures is yet to be found, state-of-the-art approaches
  demonstrated the relevance of replication strategies that bring
  content closer to consumers: The latter enjoy better response time
  while the volume of data passing through the network decreases
  overall.
  %% Although, there is no major solution to store and manipulate data in
  %% Edge infrastructures yet, existing proposals demonstrated the
  %% relevance of appropriate replication strategies to bring contents
  %% closer to consumers, reducing the impact of the latency as well as
  %% the volume of data passing through the network overall.  
  Unfortunately, locating the closest replica of a specific content
  requires indexing \emph{every live} replica along with its
  \emph{location}. 
  %
  %Current proposals built on a centralized service face scalability
  %issues, single point of failure, as well as latency penalities where
  %locating replicas may effectively take more time than actually
  %downloading contents. Instead, data consumer \processes must
  %maintain an up-to-date index themselves. Unfortunately, maintaining
  %an index of all live replicas at every \process would prove overly
  %costly in terms of memory and generated traffic, especially in large
  %scale dynamic systems where \processes create and destroy replicas
  %at any time.
  % 
  Relying on remote services for such a aim,  enters in contradiction with the
  properties of Edge infrastructures as locating replicas may
  effectively take more time than actually downloading content.  At
  the opposite, maintaining such an index at every \process would
  prove overly costly in terms of memory and traffic, especially since
  \processes can create and destroy replicas at any time.

@@

  %% \NAME is a crazy contribution
  \color{red} \NAME can constitute a novel building block for
  geo-distributed services, \eg sharing the locations of 
  web object replicas to allow nodes benefit from neighborhood downloads,
  resource discovery in the vicinity of a region, etc.

>>>>

\begin{abstract}
  %% Context and problem
  Although the holy grail to store and manipulate data in Edge
  infrastructures is yet to be found, state-of-the-art approaches
  demonstrated the relevance of replication strategies that bring
  content closer to consumers: The latter enjoy better response time
  while the volume of data passing through the network decreases
  overall.
  %% Although, there is no major solution to store and manipulate data in
  %% Edge infrastructures yet, existing proposals demonstrated the
  %% relevance of appropriate replication strategies to bring contents
  %% closer to consumers, reducing the impact of the latency as well as
  %% the volume of data passing through the network overall.  
  Unfortunately, locating the closest replica of a specific content
  requires indexing \emph{every live} replica along with its
  \emph{location}. 
  %
  %Current proposals built on a centralized service face scalability
  %issues, single point of failure, as well as latency penalities where
  %locating replicas may effectively take more time than actually
  %downloading contents. Instead, data consumer \processes must
  %maintain an up-to-date index themselves. Unfortunately, maintaining
  %an index of all live replicas at every \process would prove overly
  %costly in terms of memory and generated traffic, especially in large
  %scale dynamic systems where \processes create and destroy replicas
  %at any time.
  % 
  Relying on remote services for such a aim enters in contradiction
  with the properties of Edge infrastructures as locating replicas may
  effectively take more time than actually downloading content.  At
  the opposite, maintaining such an index at every \process would
  prove overly costly in terms of memory and traffic, especially since
  \processes can create and destroy replicas at any time.

@@

  %% \NAME is a crazy contribution
  \noindent As such, \NAME can constitute a novel building block for
  geo-distributed services, \eg by efficiently sharing the locations
  of replicated web objects in the vicinity of downloading \processes,
  or by enabling efficient resource discovery in the vicinity of a
  region.

### 2022-01-26 input/experiments.tex
mostly about abstract intro

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.

>>>>

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper.} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.

### 2022-01-26 input/introduction.tex
mostly about abstract intro

To address the aforementioned limitations, every \process that might
request or replicate content must also host its own content indexing
service in a fully decentralized fashion~\cite{kermarrec2015want}. At
any time, it can immediately locate the closest replica of specific
content.  A naive approach would be that every \process indexes and
ranks \emph{every live} replica along with its \emph{location}
information. When creating or destroying a replica, a \process would
notify all other \processes by efficiently broadcasting its
operation~\cite{birman1999bimodal, hadzilacos1994modular,
  raynal2013distributed}. Unfortunately, this also contradicts Edge
infrastructure objectives, for such a protocol does not confine the
traffic generated to maintain its indexes. A \process may acknowledge
the existence of replicas at the other side of the network while there
already exists a replica next to it.

Instead, a \process creating a replica should notify all and only
\processes that have no closer replica in the system. This would
create interconnected sets of \processes, or \emph{partitions},
gathered around a \emph{source} being their respective replica. A
\process deleting its replica should notify all members of its
partition so they can identify and rally their new closest
partition. A periodic advertisement protocol already provides both
operations for routing purposes~\cite{hemmati2015namebased}. However,
its functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item to finely tune physical-time-based intervals that depend on
  network topology parameters such as network diameter.
\end{inparaenum}

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes join, leave, and crash at any time. \NAME's efficiency
  relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.

\item [$\bullet$] We evaluate \NAME through simulations using
  PeerSim~\cite{montresor2009peersim}. Results show the consistent
  partitioning of the algorithm as well as its scalability. Using
  scoped broadcast, \NAME quickly disseminate messages to a subset of
  relevant \processes. The higher the number of partitions, the
  smaller \NAME's overhead.  Most importantly, \NAME does not generate
  traffic in quiescent systems.  % Our experiments
  %  also highlight the relevance of \NAME in autonomous systems.
  \NAME would allow to lock down the traffic generated by content
  indexing, even in contexts where \emph{physical} partitioning may
  occur.
  %As such, \NAME can constitute a new building block for
  % geo-distributed services.
\end{asparadesc}

>>>>

To address the aforementioned limitations, every \process that might
request or replicate content must also host its own content indexing
service in a fully decentralized fashion~\cite{kermarrec2015want}. At
any time, it can immediately locate the closest replica of specific
content.  A naive approach would be that every \process indexes and
ranks \emph{every live} replica along with its \emph{location}
information. When creating or destroying a replica, a \process would
notify all other \processes by broadcasting its
operation~\cite{birman1999bimodal, hadzilacos1994modular,
  raynal2013distributed}. Unfortunately, this also contradicts Edge
infrastructure objectives, for such a protocol does not confine the
traffic generated to maintain its indexes. A \process may acknowledge
the existence of replicas at the other side of the network while there
already exists a replica next to it.

Instead, a \process creating a replica should notify all and only
\processes that have no closer replica in the system. This would
create interconnected sets of \processes, or \emph{partitions},
gathered around a \emph{source} being their respective replica. A
\process deleting its replica should notify all members of its
partition so they can identify and rally their new closest
partition. Periodic advertisement protocols already provide both
operations~\cite{hemmati2015namebased, sohier2012physarum}. However,
their functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item the use of synchronous communications~\cite{sohier2012physarum}
  or physical-time-based intervals tuned according to network topology
  parameters such as network diameter~\cite{hemmati2015namebased}.
\end{inparaenum}

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes can join, leave, or crash at any time. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.

\item [$\bullet$] We evaluate \NAME through simulations using
  PeerSim~\cite{montresor2009peersim}. Results empirically show that
  \begin{inparaenum}[(i)]
  \item \NAME manages to quickly disseminate messages to the subset of
    relevant \processes;
  \item \NAME's overhead decreases when the number of partitions
    increases;
  \item \NAME does not generate traffic in quiescent systems; and
  \item \NAME enables consistent partitioning even in networks subject
    to physical partitioning.
  \end{inparaenum}
\end{asparadesc}

As such, \NAME can constitute a novel building block for
geo-distributed services, \eg by efficiently sharing the locations of
replicated web objects in the vicinity of downloading nodes, or by
enabling efficient resource discovery in the vicinity of a region.
\TODO{More detail, name drop that we can support CDN.}
